Manuscript Figures for Genome Biology

### 2018-05-21 manuscript_figures/manuscript_figures.Rmd
Heatmap improvements, adding table S3, save case study heatmaps

# remove covariates from individual cases studies that weren't informative
## TODO ##

@@

Fig4 <- plotMethodRanks(objects, colLabels = casestudy, alpha = 0.10)
Fig4
ggsave(file.path(outdir, "Figure4.pdf"), width=6, height=4)

Fig4 <- plotMethodRanks(objects, colLabels = casestudy, alpha = 0.10,
                        excludeMethods = NULL)
Fig4
ggsave(file.path(outdir, "Figure4_all.pdf"), width=6, height=4)

# heatmap : rows method, cols casestudy- one color scale 
Fig4alt <- plotMethodRanks(objects, colLabels = casestudy, alpha = 0.10, 
                        colorLow = "white", colorHigh = "blue", 
                        colorNA = "grey50")
Fig4alt
ggsave(file.path(outdir, "Figure4alt.pdf"), width=6, height=4)

##
## AR: alternative suggestion to heatmap, feel free to discard! ##
##

Fig4b <- plotMethodRanks(objects, colLabels = casestudy, alpha = 0.10,
                         linePlot = TRUE)
Fig4b
```

@@

@@

```{r}
wcs <- which(grepl("ChIPseq", casestudy))
objs <- objects[wcs]
labs <- unlist(lapply(str_split(dataset[wcs], pattern = "-benchmark.rds"), 
                      function(x) x[1]))
plotMethodRanks(objs, colLabels = labs, alpha = 0.10, xlab = "Dataset") + 
  ggtitle("ChIP-Seq")
```

```{r}
#by dataset
wcs <- which(grepl("GSEA", casestudy))
objs <- objects[wcs]
labs <- unlist(lapply(str_split(dataset[wcs], pattern = "-benchmark.rds"), 
                      function(x) x[1]))
plotMethodRanks(objs, colLabels = labs, alpha = 0.10, xlab = "Dataset") + 
  ggtitle("GSEA")
```

```{r}
# by covariate
wcs <- which(grepl("GWAS", casestudy))
objs <- objects[wcs]
labs <- unlist(lapply(str_split(dataset[wcs], pattern = "-"), 
                      function(x) x[2]))
plotMethodRanks(objs, colLabels = labs, alpha = 0.10, xlab = "Covariate",
                excludeMethods = NULL) + 
  ggtitle("GWAS")
```

```{r}
# by dataset, excluding otu when genus is available
# excluding log-ubiquity
# excluding enigma-so4 (no discoveries)
wcs <- which(grepl("microbiome", casestudy) & 
              !(grepl(c("baxter|goodrich|papa"), dataset) & 
              grepl(c("otu"), dataset)) &
              !grepl("log-ubiquity", dataset) &
              !grepl("so4", dataset))
objs <- objects[wcs]
labs <- unlist(lapply(str_split(dataset[wcs], pattern = "-benchmark.rds"), 
                      function(x) x[1]))
plotMethodRanks(objs, colLabels = labs, alpha = 0.10, xlab = "Dataset") + 
  ggtitle("Microbiome")
```

### RNA-seq
```{r}
# by dataset
wcs <- which(grepl("RNAseq", casestudy) & 
            !grepl(c("polyester|yeast"), dataset) &
            !grepl("scRNAseq", casestudy))
objs <- objects[wcs]
labs <- unlist(lapply(str_split(dataset[wcs], pattern = "-benchmark.rds"), 
                      function(x) x[1]))
plotMethodRanks(objs, colLabels = labs, alpha = 0.10, xlab = "Dataset", 
                excludeMethods = NULL) + 
  ggtitle("RNA-seq")
```

@@

# by dataset
plotMethodRanks(objs, colLabels = ds, alpha = 0.10, xlab = "Dataset") + 
  ggtitle("scRNA-seq")

# by method
plotMethodRanks(objs, colLabels = meth, alpha = 0.10, xlab = "Method") + 
  ggtitle("scRNA-seq")

# by covariate
plotMethodRanks(objs, colLabels = cv, alpha = 0.10, xlab = "Covariate") + 
  ggtitle("scRNA-seq")
```

@@

```{r}
wcs <- which(grepl("RNAseq", casestudy) & 
            !grepl(c("brain|mir|polyester|null"), dataset) &
            !grepl("scRNAseq", casestudy))
objs <- objects[wcs]
labs <- gsub(".rds", "", 
             unlist(lapply(str_split(dataset[wcs], pattern = "-results-"), 
                      function(x) x[2])))

@@

>>>>

# remove chip-seq promoter analysis (since it is the only one that uses 
# ash and we also include the csaw analysis on the same dataset).
promot <- which(grepl("promot", objects))
if (length(promot) > 0){
  objects <- objects[-promot]
}

@@

Fig4.rowOrder <- levels(plotMethodRanks(objects, colLabels = casestudy, alpha = 0.10,
                            tableOnly = TRUE)$method)
Fig4 <- plotMethodRanks(objects, colLabels = casestudy, alpha = 0.10)
Fig4
ggsave(file.path(outdir, "Figure4a.pdf"), width=6, height=4)

Fig4All.rowOrder <- levels(plotMethodRanks(objects, colLabels = casestudy, alpha = 0.10, 
                               tableOnly = TRUE, excludeMethods = NULL)$method)
Fig4All <- plotMethodRanks(objects, colLabels = casestudy, alpha = 0.10,
                        excludeMethods = NULL)
Fig4All
ggsave(file.path(outdir, "Figure4a_all.pdf"), width=6, height=4)

Extract a table of the values in Figure 4.

```{r}
# Supplementary table S3 
library(xtable)
tabS3 <- plotMethodRanks(objects, colLabels = casestudy, alpha = 0.10,
                        tableOnly = TRUE)
tabS3 <- tabS3 %>% 
  mutate(mean_prop = ifelse(is.na(mean_prop), "-",
                            paste0(round(mean_prop,2), " (", round(min_prop,2), 
                            "-", round(max_prop, 2), ")"))) %>%
  select(casestudy, method, mean_prop) %>%
  spread(casestudy, mean_prop)

xtable(tabS3)
```

Create another panel with heatmap of yeast simulation results.

# non-null
wcs <- which(grepl("RNAseq", casestudy) & 
            !grepl(c("brain|mir|null|polyester"), dataset) &
            !grepl("scRNAseq", casestudy))
objs <- objects[wcs]
labs <- gsub(".rds", "", 
             unlist(lapply(str_split(dataset[wcs], pattern = "-results-"), 
                      function(x) x[2])))

pfdr <- plotMethodRanks(objs, 
                colLabels = c("sim", "sim"), 
                alpha = 0.10, xlab = "Comparison",
                colorLow = "yellow", colorHigh = "navy",
                fill = "FDR",
                rowOrder = Fig4.rowOrder)

ptpr <- plotMethodRanks(objs, 
                colLabels = c("sim", "sim"), 
                alpha = 0.10, xlab = "Comparison",
                fill = "TPR",
                rowOrder = Fig4.rowOrder)

plot_grid(Fig4, pfdr + ylab("") + xlab(""), ptpr + ylab("") + xlab(""), 
          ncol=3, rel_widths = c(1,0.3,0.3))
ggsave(file.path(outdir, "Figure4.pdf"), width=12, height=5)

@@

```{r}
# by covariate
wcs <- which(grepl("GWAS", casestudy))
objs <- objects[wcs]
labs <- unlist(lapply(str_split(dataset[wcs], pattern = "-"), 
                      function(x) x[2]))
plotMethodRanks(objs, colLabels = labs, alpha = 0.10, xlab = "Covariate",
                excludeMethods = NULL, Nlabel = FALSE) + 
  ggtitle("GWAS")
ggsave(file.path(outdir, "FigureS1.pdf"), width=4, height=4)
```

```{r}
#by dataset
wcs <- which(grepl("GSEA", casestudy))
objs <- objects[wcs]
labs <- unlist(lapply(str_split(dataset[wcs], pattern = "-benchmark.rds"), 
                      function(x) x[1]))
plotMethodRanks(objs, colLabels = labs, alpha = 0.10, xlab = "Dataset", Nlabel = FALSE) + 
  ggtitle("GSEA")
ggsave(file.path(outdir, "FigureS2.pdf"), width=4, height=4)
```

@@

```{r}
wcs <- which(grepl("ChIPseq", casestudy))
objs <- objects[wcs]
labs <- unlist(lapply(str_split(dataset[wcs], pattern = "-benchmark.rds"), 
                      function(x) x[1]))
plotMethodRanks(objs, colLabels = labs, alpha = 0.10, xlab = "Dataset", Nlabel = FALSE) + 
  ggtitle("ChIP-Seq")
ggsave(file.path(outdir, "FigureS3.pdf"), width=5, height=4)
```

### RNA-seq
```{r}
# by dataset
wcs <- which(grepl("RNAseq", casestudy) & 
            !grepl(c("polyester|yeast"), dataset) &
            !grepl("scRNAseq", casestudy))
objs <- objects[wcs]
labs <- unlist(lapply(str_split(dataset[wcs], pattern = "-benchmark.rds"), 
                      function(x) x[1]))
plotMethodRanks(objs, colLabels = labs, alpha = 0.10, xlab = "Dataset", 
                excludeMethods = NULL, Nlabel = FALSE) + 
  ggtitle("RNA-seq")
ggsave(file.path(outdir, "FigureS4.pdf"), width=4, height=4)
```

@@

# by dataset
pa <- plotMethodRanks(objs, colLabels = ds, alpha = 0.10, xlab = "Dataset") + 
  ggtitle("scRNA-seq")

# by method
pb <- plotMethodRanks(objs, colLabels = meth, alpha = 0.10, xlab = "Method") + 
  ggtitle("scRNA-seq")

# by covariate
pc <- plotMethodRanks(objs, colLabels = cv, alpha = 0.10, xlab = "Covariate") + 
  ggtitle("scRNA-seq")

plot_grid(pa, pb, pc)
ggsave(file.path(outdir, "FigureS5.pdf"), width=8, height=5.5)
```

```{r}
# by dataset, excluding otu when genus is available
# excluding log-ubiquity
# excluding enigma-so4 (no discoveries)
wcs <- which(grepl("microbiome", casestudy) & 
              !(grepl(c("baxter|goodrich|papa"), dataset) & 
              grepl(c("otu"), dataset)) &
              !grepl("log-ubiquity", dataset) &
              !grepl("so4", dataset))
objs <- objects[wcs]
labs <- unlist(lapply(str_split(dataset[wcs], pattern = "-benchmark.rds"), 
                      function(x) x[1]))
plotMethodRanks(objs, colLabels = labs, alpha = 0.10, xlab = "Dataset", Nlabel = FALSE) + 
  ggtitle("Microbiome")
ggsave(file.path(outdir, "FigureS6.pdf"), width=7.5, height=4)
```

@@

```{r}
# non-null
wcs <- which(grepl("RNAseq", casestudy) & 
            !grepl(c("brain|mir|polyester|null"), dataset) &
            !grepl("scRNAseq", casestudy))
objs <- objects[wcs]
labs <- gsub(".rds", "", 
             unlist(lapply(str_split(dataset[wcs], pattern = "-results-"), 
                      function(x) x[2])))

plotMethodRanks(objs, 
                colLabels = labs, 
                alpha = 0.10, xlab = "Comparison",
                excludeMethods = NULL)

plotMethodRanks(objs, 
                colLabels = labs, 
                alpha = 0.10, xlab = "Comparison",
                excludeMethods = NULL, 
                fill = "FDR")

plotMethodRanks(objs, 
                colLabels = labs, 
                alpha = 0.10, xlab = "Comparison",
                excludeMethods = NULL, 
                fill = "TPR")

# null
wcs <- which(grepl("RNAseq", casestudy) & 
            !grepl(c("brain|mir|polyester|de"), dataset) &
            !grepl("scRNAseq", casestudy))
objs <- objects[wcs]
labs <- gsub(".rds", "", 
             unlist(lapply(str_split(dataset[wcs], pattern = "-results-"), 
                      function(x) x[2])))

plotMethodRanks(objs, 
                colLabels = labs, 
                alpha = 0.10, xlab = "Comparison",
                excludeMethods = NULL)

@@

plotMethodRanks(objs, 
                colLabels = labs, 
                alpha = 0.10, xlab = "Comparison",
                excludeMethods = NULL)

plotMethodRanks(objs, 
                colLabels = labs, 
                alpha = 0.10, xlab = "Comparison",
                excludeMethods = NULL, 
                fill = "FDR")

plotMethodRanks(objs, 
                colLabels = labs, 
                alpha = 0.10, xlab = "Comparison",
                excludeMethods = NULL, 
                fill = "TPR")

# null
wcs <- which(grepl("RNAseq", casestudy) & 
            !grepl(c("brain|mir|yeast|de"), dataset) &
            !grepl("scRNAseq", casestudy))
objs <- objects[wcs]
labs <- gsub(".rds", "", 
             unlist(lapply(str_split(dataset[wcs], pattern = "-results-"), 
                      function(x) x[2])))
